---
title: "\\fontsize{14pt}{3pt}\\selectfont \\textbf{\\textit{Rain in Australia - Kaggle Open Source Dataset}}"
author: "\\fontsize{12pt}{3pt}\\selectfont Luiz Guilherme Gomes Fregona"
date: "\\fontsize{12pt}{3pt}\\selectfont July, 2021"
output: 
  pdf_document:
    latex_engine: xelatex
    toc: no
    toc_depth: 3
    df_print: kable
header-includes:
  - \usepackage{fontspec}
  - \usepackage{xcolor}
  - \usepackage{titling}
  - \usepackage{booktabs}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttablex}
  - \usepackage{threeparttable}
  - \usepackage{makecell}
  - \usepackage[normalem]{ulem}
  - \setmainfont{Times New Roman}
  - \pretitle{\begin{flushleft}}
  - \posttitle{\end{flushleft}}  
  - \preauthor{\begin{flushleft}}
  - \postauthor{\end{flushleft}}  
  - \predate{\begin{flushleft}}
  - \postdate{\end{flushleft}}  
editor_options: 
  chunk_output_type: console
---
\newpage
\thispagestyle{empty}
\mbox{}

\tableofcontents
\thispagestyle{plain}

\newpage
\thispagestyle{empty}
\mbox{}

```{r, setup, include=FALSE}
knitr::opts_chunk$set(echo = T,
                      message = F,
                      warning = F,
                      error = F)
```

```{r Remove scientific notation, include=FALSE}
options(scipen = 999)
```

# 1. Introduction


# 2. Objetives



# 3. Pipeline

\newpage

# 4. Executive Summary


\newpage

# 5. Data Cleaning


\newpage

# 6. Data Exploration

\newpage

# 7. Modeling


# 8. Conclusion

Knn_imputation
Multicollinearity - Anova Test - Between categorical and numeric predictors
Outliers
preProcess - caret